PeerMind

### 2016-08-06 paper.tex
Improving math symbols.

We can represent these delegations as a graph we call \emph{delegation network} as seen in
Figure~\ref{fig:delegation-network}.
We direct edges towards a member who is delegating, to represent how their vote is computed from delegates' votes.
For example, member $M_1$ delegates the decision to members $M_0$ and $M_3$.
$M_0$ and $M_3$ become $M_1$'s delegates.
As a consequence, $M_1$'s vote ($V_{M_1}$) is computed from $M_0$'s and $M_3$'s votes ($V_{M_0}$, $V_{M_3}$).

@@

\begin{displaymath}
\mathrm{w} = \left[w_{i}\right] = \begin{dcases*}
 1 & if $M_i$ voted \\
 0 & otherwise \\
\end{dcases*},\quad \mathrm{a} = \left[a_{i}\right] = \begin{dcases*}
 1 & if $M_i$ abstained \\
 0 & otherwise \\
\end{dcases*}
\end{displaymath}

Solving $\mathrm{D} \mathbf{x_w} = \mathbf{w}$ and $\mathrm{D} \mathbf{x_a} = \mathbf{a}$ gives
us number of votes and number of abstentions, respectively, by summing together all values in the
resulting vectors: $w = \sum \mathbf{x_w}$, $a = \sum \mathbf{x_a}$.

\todo[inline]{Is the result then $\frac{\sum \mathbf{x_v}}{w}$ or $\frac{\sum \mathbf{x_v}}{\textrm{number of entries
in}~\mathbf{x_w}~\textrm{which are non-zero}}$?}

>>>>

We can represent these delegations as a graph we call \emph{delegation network} as seen in
Figure~\ref{fig:delegation-network}.
We direct edges towards a member who is delegating, to represent how their vote is computed from delegates' votes.
For example, member $M_1$ delegates the decision to members $M_0$ and $M_3$.
$M_0$ and $M_3$ become $M_1$'s delegates.
As a consequence, $M_1$'s vote $V_{M_1}$ is computed from $M_0$'s and $M_3$'s votes ($V_{M_0}$ and $V_{M_3}$).

@@

\begin{displaymath}
\mathbf{w} = \left[w_{i}\right] = \begin{dcases*}
 1 & if $M_i$ voted \\
 0 & otherwise \\
\end{dcases*},\quad \mathbf{a} = \left[a_{i}\right] = \begin{dcases*}
 1 & if $M_i$ abstained \\
 0 & otherwise \\
\end{dcases*}
\end{displaymath}

Solving $\mathrm{D} \mathbf{x_w} = \mathbf{w}$ and $\mathrm{D} \mathbf{x_a} = \mathbf{a}$ gives
us number of votes $W$ and number of abstentions $A$, respectively, by summing together all values in the
resulting vectors: $W = \sum \mathbf{x_w}$, $A = \sum \mathbf{x_a}$.

\todo[inline]{Is the result then $\frac{\sum \mathbf{x_v}}{W}$ or $\frac{\sum \mathbf{x_v}}{\textrm{number of entries
in}~\mathbf{x_w}~\textrm{which are non-zero}}$?}
